\huge A Usability Evaluation of Tor Launcher

### 2016-11-15 pets2017-paper/pets2017-paper.tex
i missed some things to remove

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
{\color {red}
The dots show the raw active configuration times,
while the boxplots show the medians and interquartile ranges.
Here, non-finishing participants' active time was computed by
subtracting the amount of time spent on the progress screen from the 
their assigned completion time of 40:08.
}
}
\label{fig:time_to_success_active_clamped}
\end{figure}

\subsection{Usability of Tor Launcher} 
{\color {red} In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.}
On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.

>>>>

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
The dots show the raw active configuration times,
while the boxplots show the medians and interquartile ranges.
Here, non-finishing participants' active time was computed by
subtracting the amount of time spent on the progress screen from the 
their assigned completion time of 40:08.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

\subsection{Usability of Tor Launcher} 
In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.
